An Infinite de Bruijn Sequence

### 2016-12-26 paper.tex
...

\begin{theorem}[Onion]
	For any $k,n \in \N$, the prefix of length $k^n-(k-1)^n$ of the sequence generated by the prefer-max construction is such that its $n$-length substrings are exactly $\{0,\dots,k\}^n \setminus \{0,\dots,k-1\}^n$, i.e., all the words of length $n$ that contain the symbol $k$. Furthermore, the suffix that begins with the 
	$(k^n-(k-1)^n+1)$th symbols is exactly the sequence generated by the prefer-max construction with the parameters $k-1$ and $n$.
\end{theorem}

This observation lead us to look at the reverse of the prefer-max sequence. The structure that we have identified means that if we somehow manage to construct the sequence backwards, we do not have to specify $k$ ahead of time because we can go on indefenitiley while $k$ grows in layers: we first write $0^n$, then a word whose substrings of length $n$ are $\{0,1\}^n$, then extend to $\{0,1,2\}^n$, and so on.

The second contribution of this work is then an efficient construction of this reversed sequence, as formulated in Algorithm~\ref{inf-construction}. Note that each step of this construction can be computed in $O(n^2)$ operations by enumerating all the $n$ rotations of $\sigma w$ and by comparing them lexicographically (reading each word from right to left).

@@

Each step of Algorithm~\ref{efficient-pref-max} can be computed in $O(n^2)$ time because it suffices to examine only $\sigma'$ which is a symbol in $\sigma w$ or is smaller by one than a symbol in this word (see Proposition~\ref{efficiency-of-pref-max} below).
The fact that this is indeed the prefer-max sequence is stated in the following theorem:

>>>>

\begin{theorem}[Onion]
	For any $k,n \in \N$, the prefix of length $k^n-(k-1)^n$ of the sequence generated by the prefer-max construction is such that its $n$-length substrings are exactly $\{0,\dots,k\}^n \setminus \{0,\dots,k-1\}^n$, i.e., all the words of length $n$ that contain the symbol $k$. Furthermore, the suffix that begins with the 
	$(k^n-(k-1)^n+1)$th symbols is exactly the sequence generated by the prefer-max construction with the parameters $k-1$ and $n$.
	\label{thm:onion}
\end{theorem}

This observation lead us to look at the reverse of the prefer-max sequence. The structure identified in Theorem~\ref{thm:onion} means that if we somehow manage to construct the sequence backwards, we do not have to specify $k$ ahead of time because we can go on indefenitiley while $k$ grows in layers: we first write $0^n$, then a word whose substrings of length $n$ are $\{0,1\}^n$, then extend to $\{0,1,2\}^n$, and so on.

The second contribution of this work is then an efficient construction of this reversed sequence. This is formulated in Algorithm~\ref{inf-construction}. Note that each step of this construction can be computed in $O(n^2)$ operations by enumerating all the $n$ rotations of $\sigma w$ and by comparing them lexicographically (reading each word from right to left).

@@

Each step of Algorithm~\ref{efficient-pref-max} can be computed in $O(n^2)$ time because it suffices to examine only $\sigma'$s which are symbols in $\sigma w$ or are a symbol that smaller by one than a symbol in $\sigma w$ (see Proposition~\ref{efficiency-of-pref-max} below).
The fact that this is indeed the prefer-max sequence is stated in the following theorem:
